Manuscript

### 2018-11-26 manuscript.Rmd
minor changes to Rmd and plots

```{r}
g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_withGroupedLineages.csv", sep = "\t", header = TRUE, row.names = 1)
g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)
g2p$Drug <- tolower(g2p$Drug)
g2p[g2p == -1] <- NA
g2p$Ref[g2p$Ref == "None"] <- NA
g2p$Alt[g2p$Alt == "None"] <- NA
g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
g2p <- subset(g2p, grepl("^CID", g2p$DrugID))

g2p_drug_genes <- unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)])
g2p_genes <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[2]))
g2p_drugs <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[1]))
g2p_genes
g2p_drugs
# Order and genes taken from pink heatmapo from Daniel's analyses
g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
```

@@

```{r}
unique(crispr_data_signif_g2p_gene$Mutation_Status_Nonsilent)
```

@@

```{r fig.height=15, fig.width=15}
crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_gene_filt, crispr_signif_g2p_lineage, by = c("Hugo_Symbol", "group_general_lineage_name"))
crispr_data_signif_g2p_lineage$Hugo_Symbol <- ordered(crispr_data_signif_g2p_lineage$Hugo_Symbol, levels = crispr_signif_g2p_20gene)

>>>>

```{r}
g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_withGroupedLineages.csv", sep = "\t", header = TRUE, row.names = 1)
g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)
g2p$Drug <- tolower(g2p$Drug)
g2p[g2p == -1] <- NA
g2p$Ref[g2p$Ref == "None"] <- NA
g2p$Alt[g2p$Alt == "None"] <- NA
g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
g2p_filt <- subset(g2p, grepl("^CID", g2p$DrugID))

g2p_drug_genes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
g2p_genes <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[2]))
g2p_drugs <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[1]))
g2p_genes
g2p_drugs
# Order and genes taken from pink heatmapo from Daniel's analyses
g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
```

```{r}
g2p_nonCID <- subset(g2p, !grepl("^CID", g2p$DrugID))
summ <- g2p_nonCID %>% group_by(Drug, DrugID) %>% tally() %>% summarize(n = n,
                                                                percent = n / 402 * 100)
summ
```

@@

@@

```{r fig.height=15, fig.width=15, eval=FALSE}
crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_gene_filt, crispr_signif_g2p_lineage, by = c("Hugo_Symbol", "group_general_lineage_name"))
crispr_data_signif_g2p_lineage$Hugo_Symbol <- ordered(crispr_data_signif_g2p_lineage$Hugo_Symbol, levels = as.character(unique((crispr_signif_g2p_lineage$Hugo_Symbol)))
